Relative-time seislet transform

### 2021-01-12 rtseis/paper.tex
Update paper.tex

%-----------------------------------------------------------------
\section{Acknowledgements}
    The research is partially supported by Texas Consortium for Computation (TCCS), the “Thousand Youth Talents Plan”, and the Starting Funds from Zhejiang University. The computational examples reported in this paper are reproducible using the \emph{Madagascar} open-source software package \cite[]{Fomel2013}.

>>>>

%-----------------------------------------------------------------
\section{Acknowledgements}
    The research is partially supported by Texas Consortium for Computation (TCCS) and the Starting Funds from Zhejiang University. The computational examples reported in this paper are reproducible using the \emph{Madagascar} open-source software package \cite[]{Fomel2013}.
